### 2016-08-14 Proofs.tex
Added missing files
Theorem 1 proof in old syntax
Theorem 2 proof in old syntax
Proof 1
Proofs
rewriting proof of Theorem 1

\section{Proofs}
\tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
\acnote{I will review for mistakes}
\input{Theorem1_FP}
\input{Theorem2_FP}
\input{Theorem3_priv}

\section{Summary of attacks(based on Bloom filter exploit) on Squid}
\acnote{For reference}\\
\heading{Crossby and Wallach: Squid Attack on hash tables} 
\begin{itemize}
\item A Squid server was ran on a stand-alone machine.
\item A file containing a list of URL's was prepared.
\item The URL requests were parsed and served by the Squid server. This completed the set-up phase.
\item Crossby and Wallach targeted hash collisions in Squid to increase the average URL load time. The authors quote ``This attack does not represent a ''smoking gun” for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks". 2 experiments were carried out to illustrate this.
\item In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's that collide with the already present URL's in the hash-table were requested. 
\item Observation: The load time of random URL's was less than the chosen URL's. It must be noted that, the authors did not use a brute-force approach to find collisions. Rather,  they proposed an efficient method to find hash-collisions. The method involves finding a set of elements that hash to the same index and using a combination of those elements to find more elements. 
\end{itemize}

>>>>

\section{Proofs}
\tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
\input{Theorem1_FP_unmerged}
\input{Theorem2_FP}
%\input{Theorem3_priv}

\iffalse
\section{Summary of attacks(based on Bloom filter exploit) on Squid}
\acnote{For reference}\\
\heading{Crossby and Wallach: Squid Attack on hash tables} 
\begin{itemize}
\item A Squid server was ran on a stand-alone machine.
\item A file containing a list of URL's was prepared.
\item The URL requests were parsed and served by the Squid server. This completed the set-up phase.
\item Crossby and Wallach targeted hash collisions in Squid to increase the average URL load time. The authors quote ``This attack does not represent a ''smoking gun'' for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks". 2 experiments were carried out to illustrate this.
\item In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's that collide with the already present URL's in the hash-table were requested. 
\item Observation: The load time of random URL's was less than the chosen URL's. It must be noted that, the authors did not use a brute-force approach to find collisions. Rather,  they proposed an efficient method to find hash-collisions. The method involves finding a set of elements that hash to the same index and using a combination of those elements to find more elements. 
\end{itemize}
